Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-17 outputs/paper/paper.qmd
Paper edits

```{r}

@@

```{r}

@@

##Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)

```{r}

>>>>

```{r}
#| label: fig-excess
#| fig-cap: "look at deez"
#| echo: false
#| message: false
#| warning: false

@@

```{r}
#| label: fig-statements
#| fig-cap: "look at dat"
#| echo: false
#| message: false
#| warning: false

survey_2 <- survey_data[survey_data$wave == 2,]

@@

\## Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)

```{r}
#| label: tbl-mate
#| fig-cap: "look at dat"
#| echo: false
#| message: false
#| warning: false
